CONEM2024-0025\\ NEW ABC MULTICRITERIA CLASSIFICATION WITH ANALYTICAL HIERARCHY PROCESS: HOW TO ATTRIBUTE WEIGHTS AND FORCE CONSISTENCY OF PAIRWISE COMPARISONS MATRIX

### 2024-03-15 accepted/CONEM2024/FCPCOM/CONEM2024.tex
ACKNOWLEDGEMENTS revised

Huge thanks to the teams responsible for developing elementary OS, as well as yandex translator, grammarly, duckduckgo, gummi, CodeBlocks, git, GitHub, gcc, and TeXLive libraries. Without the availability of these tools, the 'COPSolver's library for solving the multicriteria classification problem' could never have been developed. I am also very grateful to my co-workers Regilda da Costa e Silva Menêzes and Marcos Luiz Henrique for their constant support to the projects I develop and to my dear advisees , among others, for having participated so enthusiastically in the projects that gave rise to this software, in particular for having made the effort to describe real processes in such detail. I would also like to thank the company in the plastic bag sector and other companies that made the studies possible as well as the identification of the new optimization problem addressed in COPSolver\_1.0-1. \\

        Se houver, esta seção deve ser colocada antes da lista de referências.

>>>>

Huge thanks to the teams responsible for developing elementary OS, CodeBlocks, git, GitHub, gcc, TeXLive libraries, duckduckgo, gummi, Yandex translator, and Grammarly. Without the availability of these tools, this paper and the "COPSolver's library for solving the multicriteria classification problem" could never have been developed. I am also very grateful to my co-workers Regilda da Costa e Silva Menêzes and Marcos Luiz Henrique for their constant support for my projects and to my dear advisees Betriz Marinho Cavalcanti, Alexia Maria Duque Silva and Erika Leticia Rodrigues Silva for having participated so enthusiastically in this project, in particular for having made such effort to collect all the necessary data for this study. I would also like to thank the three companies that provided all the essential information we needed for the correct development of this work. \\
